---
title: "Week 5 - Experimenting - Homework"
author: "Kovács Ádám József. Nguyen Nam Son"
date: "08/10/2020"
output: html_document
---

<br>

## Loading the data...

```{r setup, message = FALSE, warning = FALSE}

library(data.table)
library(magrittr)
library(ggplot2)
library(scales)

wd = file.path("~", "eltecon-datascience")
setwd(wd)

xp = fread("experiment_result_HW.csv")

```

<br>

## Calculating the uplift for KPI the view rate

```{r uplift1, message = FALSE, warning = FALSE}
# calculating uplift for 1st
view_rate_xp1 = xp[period == "first period"] %>% .[, .(view_rate = sum(has_viewed_website) / .N), by = group]
dcast(view_rate_xp1, .~group) %>% .[, (treatment / control) -1] %>% paste("The uplift for the first period is",percent(.))
                                
# for second
view_rate_xp2 = xp[period == "second period"] %>% .[, .(view_rate = sum(has_viewed_website) / .N), by = group]
dcast(view_rate_xp2, .~group) %>% .[, (treatment / control) -1] %>% paste("The uplift for the second period is",percent(.))

#for full period
view_rate_f = xp[, .(view_rate = sum(has_viewed_website) / .N), by = group]
dcast(view_rate_f, .~group) %>% .[, (treatment / control) -1] %>% paste("The uplift for the full period is",percent(.))

xpn = xp[, .(.N, mean(has_viewed_website)), keyby = .(period, group)]
xp[, .(.N, mean(has_viewed_website)), group]
```
<br>

## Plot the sample sizes in each period

```{r size1, message = FALSE, warning = FALSE}

ggplot(aes(period, N, fill = group), data = xpn) +
  geom_col(position = "dodge") +
  labs(title = "Sample size distribution across periods",
       subtitle = "The treatment group is underrepresented in the first period.",
       caption = "Made by Á.Kovács and S.N.Nguyen",
       x = element_blank(),
       y = "Number of contacted people") +
  theme_classic() +
  geom_label(aes(label = N), vjust = 2.5, position = position_dodge(0.9), color = "white", fontface = "bold", size = 4, show.legend = FALSE)

```
<br>

## Recalculate the weighted uplifts

```{r weighted uplift1, message = FALSE, warning = FALSE}
# calculating weighted uplift for 1st

KPIt1 = xpn$V2[2]*100000
KPIc1 = xpn$V2[1]*100000

paste("The weighted uplift for the first period is", percent(KPIt1 / KPIc1 - 1))

# for second
KPIt1 = xpn$V2[4]*100000
KPIc1 = xpn$V2[3]*100000

paste("The weighted uplift for the second period is", percent(KPIt1 / KPIc1 - 1))

#for full period
KPIt = (xpn$V2[2]*100000 + xpn$V2[4]*100000)
KPIc = (xpn$V2[1]*100000 + xpn$V2[3]*100000)

paste("The weighted uplift for the full period is", percent(KPIt / KPIc - 1))

```
<br>

## Plot KPIs over period

```{r over1, message = FALSE, warning = FALSE}

ggplot(aes(period, V2, fill = group),data = xpn) +
  geom_col(position = "dodge") +
  labs(title = "KPIs across periods",
       subtitle = "The view rate in each period for each group",
       caption = "Made by Á.Kovács and S.N.Nguyen",
       x = element_blank(),
       y = "Share of contacts with views") +
  scale_y_continuous(labels = scales::percent) +
  theme_classic() +
  geom_label(aes(label = percent(V2)), vjust = 2.5, position = position_dodge(0.9), color = "white", fontface = "bold", size = 4, show.legend = FALSE)

```
<br>

## Plot the KPIs for the full period

```{r full1, message = FALSE, warning = FALSE}

ggplot(aes(group, view_rate, fill = group),data = view_rate_f) +
  geom_col(show.legend = FALSE) +
  labs(title = "KPIs for full period",
    subtitle = paste("The weighted uplift for the whole period is", percent((KPIt / KPIc - 1))),
    caption = "Made by Á.Kovács and S.N.Nguyen",
    x = element_blank(),
    y = "Share of contacts with views") +
  scale_y_continuous(labels = scales::percent) +
  theme_classic() +
  geom_label(aes(label = percent(view_rate)), vjust = 2.5, position = position_dodge(0.9), color = "white", fontface = "bold", size = 4, show.legend = FALSE)

```
<br>

## Calculating the uplift for the KPI of rate of items ordered 

```{r uplift2, message = FALSE, warning = FALSE}
# calculating uplift for 1st
item_rate_xp1 = xp[period == "first period"] %>% .[, .(item_rate = sum(num_items_ordered) / .N), by = group]
dcast(item_rate_xp1, .~group) %>% .[, (treatment / control) -1] %>% paste("The uplift for the first period is",percent(.))
                                
# for second
item_rate_xp2 = xp[period == "second period"] %>% .[, .(item_rate = sum(num_items_ordered) / .N), by = group]
dcast(item_rate_xp2, .~group) %>% .[, (treatment / control) -1] %>% paste("The uplift for the second period is",percent(.))

#for full period
item_rate_f = xp[, .(item_rate = sum(num_items_ordered) / .N), by = group]
dcast(item_rate_f, .~group) %>% .[, (treatment / control) -1] %>% paste("The uplift for the full period is",percent(.))

xpm = xp[, .(.N, mean(num_items_ordered)), keyby = .(period, group)]
xp[, .(.N, mean(num_items_ordered)), group]
```
<br>

## Recalculate the weighted uplifts

```{r weighted uplift2, message = FALSE, warning = FALSE}
# calculating weighted uplift for 1st

KPIt1 = xpm$V2[2]*100000
KPIc1 = xpm$V2[1]*100000

paste("The weighted uplift for the first period is", percent(KPIt1 / KPIc1 - 1))

# for second
KPIt1 = xpm$V2[4]*100000
KPIc1 = xpm$V2[3]*100000

paste("The weighted uplift for the second period is", percent(KPIt1 / KPIc1 - 1))

#for full period
KPIt = (xpm$V2[2]*100000 + xpm$V2[4]*100000)
KPIc = (xpm$V2[1]*100000 + xpm$V2[3]*100000)

paste("The weighted uplift for the full period is", percent(KPIt / KPIc - 1))

```

<br>

## Plot the KPIs for the full period

```{r full2, message = FALSE, warning = FALSE}

ggplot(aes(group, item_rate, fill = group),data = item_rate_f) +
  geom_col(show.legend = FALSE) +
  labs(title = "KPIs for full period",
    subtitle = paste("The weighted uplift for the whole period is", percent((KPIt / KPIc - 1))),
    caption = "Made by Á.Kovács and S.N.Nguyen",
    x = element_blank(),
    y = "Average number of items ordered per person") +
    theme_classic() +
  geom_label(aes(label = round(item_rate ,3)), vjust = 2.5, position = position_dodge(0.9), color = "white", fontface = "bold", size = 4, show.legend = FALSE)

```

<br>

## Calculating the uplift for KPI of sales amount rate
 
```{r uplift3, message = FALSE, warning = FALSE}
# calculating uplift for 1st
sales_rate_xp1 = xp[period == "first period"] %>% .[, .(sales_rate = sum(sales_amount) / .N), by = group]
dcast(sales_rate_xp1, .~group) %>% .[, (treatment / control) -1] %>% paste("The uplift for the first period is",percent(.))
                                
# for second
sales_rate_xp2 = xp[period == "second period"] %>% .[, .(sales_rate = sum(sales_amount) / .N), by = group]
dcast(sales_rate_xp2, .~group) %>% .[, (treatment / control) -1] %>% paste("The uplift for the second period is",percent(.))

#for full period
sales_rate_f = xp[, .(sales_rate = sum(sales_amount) / .N), by = group]
dcast(sales_rate_f, .~group) %>% .[, (treatment / control) -1] %>% paste("The uplift for the full period is",percent(.))

xpo = xp[, .(.N, mean(sales_amount)), keyby = .(period, group)]
xp[, .(.N, mean(num_items_ordered)), group]
```
<br>

## Recalculate the weighted uplifts

```{r weighted uplift3, message = FALSE, warning = FALSE}
# calculating weighted uplift for 1st

KPIt1 = xpo$V2[2]*100000
KPIc1 = xpo$V2[1]*100000

paste("The weighted uplift for the first period is", percent(KPIt1 / KPIc1 - 1))

# for second
KPIt1 = xpo$V2[4]*100000
KPIc1 = xpo$V2[3]*100000

paste("The weighted uplift for the second period is", percent(KPIt1 / KPIc1 - 1))

#for full period
KPIt = (xpo$V2[2]*100000 + xpo$V2[4]*100000)
KPIc = (xpo$V2[1]*100000 + xpo$V2[3]*100000)

paste("The weighted uplift for the full period is", percent(KPIt / KPIc - 1))

```
<br>

## Plot the KPIs for the full period

```{r full3, message = FALSE, warning = FALSE}

ggplot(aes(group, sales_rate, fill = group),data = sales_rate_f) +
  geom_col(show.legend = FALSE) +
  labs(title = "KPIs for full period",
    subtitle = paste("The weighted uplift for the whole period is", percent((KPIt / KPIc - 1))),
    caption = "Made by Á.Kovács and S.N.Nguyen",
    x = element_blank(),
    y = "Average sales per person") +
    theme_classic() +
  geom_label(aes(label = round(sales_rate ,3)), vjust = 2.5, position = position_dodge(0.9), color = "white", fontface = "bold", size = 4, show.legend = FALSE)

```

## Assessment



***